When the Pen Becomes a Sword: Retired US Military Officers and Op-Ed Use in Contemporary America

### 2020-07-15 code/Submissionv1.Rmd
commit changes

```{r, include = FALSE, echo = FALSE}
library("here")       # file paths
library("tidyverse")  # workhorse package
library("tidylog")
library("kableExtra")
library("knitr")
library("ggdag")
library("dagitty")
```

@@

```
The degree and character of political polarization in a society also has the potential to impact the professionalism of the military as an institution. To understand how, recall that the three salient characteristics of the political polarization prevalent in contemporary America include an increase in the number and scope of issues that have become polarized (the phenomenon referred to as "conflict extension" [@layman_party_2002]), an increase in the strength of negative feelings held by supporters of an issue toward the opposition (the rise of "negative partisanship" [@abramowitz_great_2018]), and an increase in the salience of core issues related to individual and national identity [@white_values_2002; @mann_its_2012; @sides_identity_2018]. These three characteristics convey several implications for the military as an institution and its leaders.

@@

**$H_1$: The majority of op-eds published by retired military officers over the time period examine will be apolitical and non-partisan in tone.**

**$H_2$: Because overall newspaper consumption has dropped in the past 40 years, there will be fewer opinion pieces over time authored by military officers.**

**$H_3$: Given that polarization has become increasingly pronounced in the United States in recent years, there will be an increase in the number of op-eds which reveal political and partisan sentiments (indication of a drop in professionalism).**

@@

```{r code, include=FALSE, echo=FALSE}
# Create a Variable Called case-count that counts the number of times by publishing year an article published 
# regarding social policy or general parties or parties by name or administrations occurs
rem_obs %>% group_by(PubYr) %>% 
  mutate(
    case_count=sum(MilPSoc ==1 | Dom_P==1 | Fig_Nme==1) 
  ) %>% view()
```
\doublespace

A couple of interesting observations are worth noting about the data in Table 2. First, one can quickly observe that there appear to be three distinct clusters of observations with respect to publishing year. The first occurs in the time frame between roughly 1998-1999, the second between 2004-2007, and the third between 2016-2019. The clusters can also be seen in time in Figure 1 on the following page.

@@

```{r fig2, fig.height=4, fig.width=5, fig.align="center", include=TRUE, echo=FALSE}
datatograph <- data.frame(
  year=c("1994","1996","1998","1999","2000","2003", "2004", "2006", "2007", "2010", "2013","2014", "2016", "2017", "2018", "2019", "2020"), count=c(1, 1,2, 3, 1, 1, 3, 3, 3, 1, 1, 1, 6, 5, 4, 6, 1)
)
ggplot(datatograph, aes(x =year, y =count)) + geom_bar(stat = "identity", width=.2) +
  labs(
    x = "Year",
    y = "Count",
    color = NULL,
    title = "Figure 2: # of Op-Eds Written By Military Retirees",
    subtitle = "On Topics of Social Policy, Domestic Policy, or Individual Figures"
  )
```

@@

Using these characteristics as guidelines, I therefore develop two new variables. The first is **Result**, which can take on the following values:\singlespace
* **Permissible** -if the reader cannot clearly draw conclusions regarding the author's political stances or partisan preferences; or if the topic addressed in the publication in fact does in fact fall underneath the area of clear military expertise.
* **Questionable** -if the reader can draw some general, but not final, conclusions regarding the author's political stances or partisan preferences; or if the topic addressed in the publication is questionably an area of reasonable military expertise.
* **Inappropriate** -if the reader can draw clear conclusions regarding the author's partisan preferences or political leanings; or if the author addresses a topic that is not an area considered to be directly relevant to military expertise, or a matter that the military should judge.

@@

```{r fig4, fig.height=4, fig.width=5, fig.align="center", include=TRUE, echo=FALSE}
datatograph <- data.frame(
  decade=c("1979-1989", "1989-1999", "1999-2009", "2009-2019" ), numcount=c(13, 51, 102, 161)
)
ggplot(datatograph, aes(x =decade, y =numcount)) + geom_bar(stat = "identity", width=.2) +
  labs(
    x = "Period",
    y = "Published Opinion Pieces",
    color = NULL,
    title = "Figure 4: Total Number of Op-Eds Written By Military Retirees",
    subtitle = "WSJ, NY Times, Washington Post, USA Today, and LA Times"
  )
```

>>>>

```{r, include = FALSE, echo = FALSE}
library("here")       # file paths
library("tidyverse")  # workhorse package
library("tidylog")
library("kableExtra")
library("knitr")
library("ggdag")
library("dagitty")
library("gridExtra")
```
\newpage

@@

The degree and character of political polarization in a society also has the potential to impact the professionalism of the military as an institution. To understand how, recall that the three salient characteristics of the political polarization prevalent in contemporary America include an increase in the number and scope of issues that have become polarized (the phenomenon referred to as "conflict extension" [@layman_party_2002]), an increase in the strength of negative feelings held by supporters of an issue toward the opposition (the rise of "negative partisanship" [@abramowitz_great_2018]), and an increase in the salience of core issues related to individual and national identity [@white_values_2002; @mann_its_2012; @sides_identity_2018]. These three characteristics convey several implications for the military as an institution and its leaders.

@@

_$H_1$: The majority of op-eds published by retired military officers over the time period examine will be apolitical and non-partisan in tone._

_$H_2$: Because overall newspaper consumption has dropped in the past 40 years, there will be fewer opinion pieces over time authored by military officers._

_$H_3$: Given that polarization has become increasingly pronounced in the United States in recent years, there will be an increase in the number of op-eds which reveal political and partisan sentiments (indication of a drop in professionalism)._

@@

```{r code, include=FALSE, echo=FALSE}
# Create a Variable Called case-count that counts the number of times by publishing year an article published 
# regarding social policy or general parties or parties by name or administrations occurs
adj2dataset <- adjdataset %>% group_by(PubYr) %>% 
  mutate(
    case_count=sum(MilPSoc ==1 | Dom_P==1 | Fig_Nme==1), 
    yr_total_count=sum(War_Ops==1 | Trp_Clt==1| Str_Adv==1 | MilPSoc ==1 | Dom_P==1 | Fig_Nme==1),
    prop_yr=(case_count/yr_total_count)
  ) %>% view()
```
\doublespace

A couple of interesting observations are worth noting about the data in Table 2. First, one can quickly observe that there appear to be three distinct clusters of observations with respect to publishing year. The first occurs in the time frame between roughly 1998-1999, the second between 2004-2007, and the third between 2016-2019. The clusters can also be seen in time in Figure 2 on the following page.

@@

```{r fig2, fig.height=4, fig.width=6, fig.align="center", include=TRUE, echo=FALSE}
datatograph <- data.frame(
  year=c("1994","1996","1998","1999","2000","2003", "2004", "2006", "2007", "2010", "2013","2014", "2016", "2017", "2018", "2019", "2020"), count=c(1, 1,2, 3, 1, 1, 3, 3, 3, 1, 1, 1, 6, 5, 4, 6, 1)
)
ggplot(datatograph, aes(x =year, y =count)) + geom_bar(stat = "identity", width=.2) +
  labs(
    x = "Year",
    y = "Count",
    color = NULL,
    title = "Figure 2: # of Op-Eds Written By Military Retirees",
    subtitle = "On Topics of Social Policy, Domestic Policy, or Political Administrations/Figures"
  )
```

```{r practice, include = TRUE, echo=FALSE}

plot1<- ggplot(data=adj2dataset, mapping=aes(x=PubYr, y=case_count)) + geom_point() + geom_smooth() + labs(x="Year", y="Count", color=NULL, title="Figure 2: Yearly # of Op-Eds Published by Retired Military Officers", subtitle="On Topics of Social Policy, Domestic Policy, or Political Administrations/Figures")
plot2 <- ggplot(data=adj2dataset, mapping=aes(x=PubYr, y=prop_yr)) + geom_point() + geom_smooth() + labs(x="Year", y="Count", color=NULL, title="Figure 2: Proportion of Total Op-Eds Published by Retired Military Officers ", subtitle="On Topics of Social Policy, Domestic Policy, or Political Administrations/Figures")
grid.arrange(plot1, plot2, ncol=2)
```

@@

Using these characteristics as guidelines, I therefore develop two new variables. The first is **Result**, which can take on the following values:
\singlespace
* **Permissible** -if the reader cannot clearly draw conclusions regarding the author's political stances or partisan preferences; or if the topic addressed in the publication in fact does in fact fall underneath the area of clear military expertise.
* **Questionable** -if the reader can draw some general, but not final, conclusions regarding the author's political stances or partisan preferences; or if the topic addressed in the publication is questionably an area of reasonable military expertise.
* **Inappropriate** -if the reader can draw clear conclusions regarding the author's partisan preferences or political leanings; or if the author addresses a topic that is not an area considered to be directly relevant to military expertise, or a matter that the military should judge.

@@

```{r fig4, fig.height=4, fig.width=5, fig.align="center", include=TRUE, echo=FALSE}
datatograph <- data.frame(
  decade=c("1979-1989", "1989-1999", "1999-2009", "2009-2019" ), numcount=c(13, 51, 102, 161)
)
ggplot(datatograph, aes(x =decade, y =numcount)) + geom_bar(stat = "identity", width=.2) +
  labs(
    x = "Period",
    y = "Published Opinion Pieces",
    color = NULL,
    title = "Figure 4: # of Op-Eds Written By Military Retirees",
    subtitle = "Published in WSJ, NY Times, Wa Post, USA Today, and LA Times"
  )
```
